---
title: "My Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Testing R Markdown

### Header 3

Write some sample text here. **Bold text**

-   apple
-   banana
-   list one
-   list two
-   new
-   old

*this is my italic text*

*but wait there's more*

1.  First item in ordered list
2.  Second item in ordered list

# H1

## subheader

```{r}
x <- 4*3
```

---

# Introduction

* read in data

```{r}
bg_chem <- read.csv("../data/BGchem2008data.csv")
```

# Analysis

calculate summary statistics

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```

calculate mean Redfield ratio

```{r}
ratio <- (nitrate + nitrite + amm)/phos
```

# Plots

```{r, echo=FALSE}
plot(bg_chem$CTD_Depth,bg_chem$CTD_Temperature)
```

plot Redfield ratio

```{r, echo=FALSE}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```

***

TIL... 

text files are good for git and github
powerpoint not so much, binaries not so much
you can create a project in RStudio, turn on Git for version control, and upload it to Github and then create a repository with it!
